**Tooltips_and_Popovers: Tooltips and Popovers**

## **Description**

Tooltips and Popovers allow you to add additional information about controls or outputs without cluttering up your user interface. You can add a tooltip to a button that displays on hover and better explains what the button will do, or you could add a popover to an output providing further analysis of that output.

## **Components**

There are eight functions in the Tooltips and Popovers family:

[**`bsTooltip`**](https://www.rdocumentation.org/link/bsTooltip?package=shinyBS&version=0.61.1)

:   Used in the UI to add a tooltip to an element in your UI.

[**`bsPopover`**](https://www.rdocumentation.org/link/bsPopover?package=shinyBS&version=0.61.1)

:   Used in the UI to add a popover to an element in your UI.

[**`tipify`**](https://www.rdocumentation.org/link/tipify?package=shinyBS&version=0.61.1)

:   Wrap any UI element in **`tipify`** to add a tooltip to the wrapped element. Preferred for elemented created with [**`renderUI`**](https://www.rdocumentation.org/link/renderUI?package=shinyBS&version=0.61.1).

[**`popify`**](https://www.rdocumentation.org/link/popify?package=shinyBS&version=0.61.1)

:   Wrap any UI element in **`popify`** to add a popover to the wrapped element. Preferred for elements created with [**`renderUI`**](https://www.rdocumentation.org/link/renderUI?package=shinyBS&version=0.61.1).

[**`addTooltip`**](https://www.rdocumentation.org/link/addTooltip?package=shinyBS&version=0.61.1)

:   Used in the Server logic to add a tooltip to an element in your UI.

[**`addPopover`**](https://www.rdocumentation.org/link/addPopover?package=shinyBS&version=0.61.1)

:   Used in the Server logic to add a popover to an element in your UI.

[**`removeTooltip`**](https://www.rdocumentation.org/link/removeTooltip?package=shinyBS&version=0.61.1)

:   Used in the Server logic to remove a tooltip from an element in your UI.

[**`removePopover`**](https://www.rdocumentation.org/link/removePopover?package=shinyBS&version=0.61.1)

:   Used in the Server logic to remove a popover from an element in your UI.

```{r}
if(!require('shinyBS')) {
    install.packages('shinyBS')
    library('shinyBS')
}
```

```{r}
library(shiny)
library(shinyBS)

app = shinyApp(
 ui =
 fluidPage(
   sidebarLayout(
     sidebarPanel(
       sliderInput("bins",
                   "Number of bins:",
                   min = 1,
                   max = 50,
                   value = 30),
       bsTooltip("bins", "The wait times will be broken into this many equally spaced bins",
         "right", options = list(container = "body"))
     ),
     mainPanel(
       plotOutput("distPlot"),
       uiOutput("uiExample")
     )
   )
 ),
 server =
 function(input, output, session) {
   output$distPlot <- renderPlot({

     # generate bins based on input$bins from ui.R
     x    <- faithful[, 2]
     bins <- seq(min(x), max(x), length.out = input$bins + 1)

     # draw the histogram with the specified number of bins
     hist(x, breaks = bins, col = 'darkgray', border = 'white')

   })
   output$uiExample <- renderUI({
     tags$span(
       popify(bsButton("pointlessButton", "Button", style = "primary", size = "large"),
         "A Pointless Button",
         "This button is <b>pointless</b>. It does not do <em>anything</em>!"),
       tipify(bsButton("pB2", "Button", style = "inverse", size = "extra-small"),
         "This button is pointless too!")
     )
   })
   addPopover(session, "distPlot", "Data", content = paste0("<p>Waiting time between ",
     "eruptions and the duration of the eruption for the Old Faithful geyser ",
     "in Yellowstone National Park, Wyoming, USA.</p><p>Azzalini, A. and ",
     "Bowman, A. W. (1990). A look at some data on the Old Faithful geyser. ",
     "Applied Statistics 39, 357-365.</p>"), trigger = 'click')
 }
)
 runApp(app)

```

You can create tooltips and popovers from either the UI script or within the Server logic. [**`bsTooltip`**](https://www.rdocumentation.org/link/bsTooltip?package=shinyBS&version=0.61.1) and [**`bsPopover`**](https://www.rdocumentation.org/link/bsPopover?package=shinyBS&version=0.61.1) are used in the UI, and [**`addTooltip`**](https://www.rdocumentation.org/link/addTooltip?package=shinyBS&version=0.61.1) and [**`addPopover`**](https://www.rdocumentation.org/link/addPopover?package=shinyBS&version=0.61.1) are used in the Server logic. [**`tipify`**](https://www.rdocumentation.org/link/tipify?package=shinyBS&version=0.61.1) and [**`popify`**](https://www.rdocumentation.org/link/popify?package=shinyBS&version=0.61.1) can be used within the UI or from within a [**`renderUI`**](https://www.rdocumentation.org/link/renderUI?package=shinyBS&version=0.61.1) in the Server logic. They also have the added advantage of not requiring that the UI element have an ID attribute.

```{r}
library(shiny)
library(DT)

shinyApp(
  ui = fluidPage(
    dataTableOutput('table'),
    verbatimTextOutput('hoverIndex')
  ),

  server = function(server, input, output) {

    output$hoverIndex <- renderText({
      paste("hover column info", input$hoverIndexJS)
    })

    output$table <- renderDataTable({
      datatable(data.frame(`A` = 1:5, `B` = 11:15, `C` = LETTERS[1:5]),
                rownames = F,
                callback = JS("
                  table.on('mouseenter', 'td', function() {
                    Shiny.onInputChange('hoverIndexJS', this.innerHTML);
                  });
                  return table;
                ")
      )
    })
  }
)
```
